---
title: 'ETC5513: Collaborative and Reproducible Practices'
subtitle: "Assignment 3"
author: "Michael Lydeamore"
date: today
format:
    html:
        embed-resources: true
---


```{r setup}
#| include: false
#| eval: true
source("setup.R")
```

```{r}
#| echo: false

total_marks <- 0

add_marks <- function(amount) {
    total_marks <<- total_marks + amount

    amount
}

```

```{r, echo = FALSE, eval = file.exists("tutorial.css")}
htmltools::includeCSS("tutorial.css")
```


## `r emo::ji("target")` Objectives

* Working on a reproducible  Rstudio project
* Produce a pdf report using the template discussed in Week 7 or Week 8.
* Practice markdown syntax
* Practice R coding
* Use R chunk options to customize your report template
* Create  tables, add table captions and  refer to them in the report text as described in Week 4
* Create simple figures to visualize the data, add figure captions and  refer to the figures in the report text as you learned in Week 4
* Demonstrate that you are able to work in groups to clone a GitHub repository locally and synchronize the changes between your local and remote repositories while using individual branches.
* Show that you can create and merge branches as well as resolve conflicts.
* Show that you can create meaningful Git commits so that the changes and the history of the project can be recorded and tracked.

::: {.callout-important}
This is an **individual**  and **group** assignment.

The printed final PDF report cannot exceed 16 pages for teams of four or 20 pages for teams of five (not including appendix pages). Additionally, you cannot use a dataset that has been previously used for other assignments or in other units this year or previous years.

You cannot use a dataset that has been used for another assignment.
:::

## Part A

::: {.callout-important}
Join the GitHub Classroom for this assignment [here](https://classroom.github.com/a/90isL5_2).

**You can choose your own group name, but make sure to submit it on the Google Form [here](https://forms.gle/qdEU7eYCsLZhRyV29)**
:::


As a group, you need to agree on a topic, and select a dataset or several datasets for the assignment. You should decide how to divide up the work between you.

You should create branches for various sections of the report (for example, Executive Summary, Methods, Figures). Each of you can work on more than one section.


- Title and authors
- Table of contents: Defining using adequate YAML syntax
- Executive summary: Maximum of 4 sentences
- Introduction: Maximum 10 sentences
- The body of the report should contain the following sections:
    - Methodology: Maximum 300 words
        - Should include a figure and a table and those must be referenced in the text and have adequate captions 
    - Results: Maximum 200 words. Should include either a figure **or** a table.
    - Discussion, conclusion and recommendations
    - Reference section: Include at least 1 reference. 

## Part B

As a team, you need to:

1. Merge the branches: Start by merging all the branches into the main branch. You will need to get organized and do this one by one so that you can resolve the conflicts that will appear.
2. Resolve conflicts: Since you will be working on the same sections, conflicts may arise when the same lines of code are modified in different branches. To resolve conflicts, edit the affected files and choose which version to keep. Once you have resolved the conflicts, commit the changes.
3. Make sure that the report renders into a pdf without errors each time you do a merge. If errors arise please solve them.
4. Review and Revise: Carefully review the final report to ensure that it meets all the requirements of a cohesive report and is free of errors. Make any necessary revisions and edits before submitting the report. For this, you will all probably need to work on the main branch. Please ensure that any changes made are in terms of the requirements and in a coordinated fashion to avoid any problems.

The final business report must look professional, coherent and connected.

Students who do not participate in Part B will receive a grade of 0 for the assignment.

**Teams will not be penalised if individual students do not contribute to to the work on their respective branches**.

## Assignment Submission

The report must be rendered to PDF. Code outputs do _not_ need to be visible - you are creating a clean business report, so only include them in they are adding to your narrative.

::: {.callout-important}
The printed final PDF report cannot exceed 16 pages for teams of three or 20 pages for teams of four (not including appendix pages)
:::

# Part C - Slides

Create a maximum 10 slide summary of your group report. The slides must be _fully reproducible_. You should make a new `qmd` in the same repo you've used for Parts A and B. You will present these slides _as a group_ in your tutorials in Week 12.

**The presentations have a _maximum_ time of 10 minutes**


The slide format should be as follows:

* Title slide. Include your name and the title of your report at a minimum.
* Problem introduction.
* Dataset description
* Methods
* Results
* Conclusions and/or recommendations

It is up to you to decide how many slides to allocate to each section.

You may choose whether to include the R code output in your presentation or not. However, please keep in mind that we are looking for a professional and cohesive presentation, which may mean the code does not get shown.

Make sure to commit frequently, not just at the end of the work!


## Marking Rubric

In addition to the points for each section as described above, you will be graded on your:

### Part A:

- Report template (`r add_marks(2)` points). The default Quarto template will be granted 1 point. Remember, styling that takes away from the report _is not beneficial_.
- Issues with spelling and grammar (up to -3pts)
- Messages in commits are clear and informative (`r add_marks(2)` points)

### Part B:

- Methodology no more than 300 words (`r add_marks(1)` points)
- Methodology includes a figure and table, both referenced in text, with captions (`r add_marks(2)` points)
- Results no more than 200 words (`r add_marks(1)` points)
- Results contains figure and/or table, referenced in text, with caption (`r add_marks(2)` points)
- Report quality: Sections in the report are connected and aligned with the research question in a coherent way (`r add_marks(2)` points).
- References included (`r add_marks(1)` points)
- Branches successfully merged (`r add_marks(3)` points)
- Conflicts resolved (`r add_marks(2)` points)
- Report is reproducible (`r add_marks(2)` points)
- Format followed (`r add_marks(3)` points)
- Table of contents using YAML (`r add_marks(1)` points)
- R code style (`r add_marks(2)` points)
- Reproducible tooling (`r add_marks(2)` points):
    - `gitignore`
    - issues
    - `renv`
    - Or other tools

### Part C:

* Presentation is reproducible  (`r add_marks(2)` points)
* Styling is sensible and does not detract from the presentation  (`r add_marks(1)` points)
* Presentation tells a clear story  (`r add_marks(2)` points)
* Presentation follows the required format (`r add_marks(2)`)

Maximum grade: `r total_marks` points.

## Assignment Submission

The presentations will take place in your tutorials in Week 12.

Marking for Parts A & B will take place directly on GitHub classroom.

## Plagiarism

Monash University is committed to honesty and academic integrity. There are serious consequences for plagiarism and collusion. If plagiarism and/or collusion is detected further actions will be taken according to Monash University policy and procedures. More info here:

https://www.monash.edu/students/admin/policies/academic-integrity

You cannot re-use assignments that have been submitted or used in other units.