---
title: 'ETC5513: Collaborative and Reproducible Practices'
subtitle: "Assignment - Oral Presentation"
author: "Michael Lydeamore"
date: today
format:
    html:
        embed-resources: true
---


```{r setup}
#| include: false
#| eval: true
source("setup.R")
```

```{r}
#| echo: false

total_marks <- 0

add_marks <- function(amount) {
    total_marks <<- total_marks + amount

    amount
}

```

```{r, echo = FALSE, eval = file.exists("tutorial.css")}
htmltools::includeCSS("tutorial.css")
```


## Objectives

* Demonstrate an understanding of `git` workflows
* Communicate technical ideas clearly and effectively

::: {.callout-important}
This is an **individual**  assignment.
:::

## Instructions

Create a **10 minute maximum** video that answers the following questions:

---

1. **What happens when two people edit the same file?**  
   How does `git` handle that, and what do you need to do?

2. **How does `git` help you recover from mistakes?**  
   Explain how you would undo a bad commit, and how that might differ depending on the situation.

Throughout the video, you should share/record your screen and have you camera visible. You are welcome to use the screen for demonstrating the concepts you are explaining.

---

Your goal is not just to show what to do, but to explain **why** you’re doing it. For example:

>  "We revert this commit instead of resetting because the commit has already been pushed and we don’t want to rewrite public history."

---

::: {.callout-important}
You **cannot speed up** your recording — it must be delivered in real time to ensure you're within the time limit.
:::

## Submission

Please upload the completed video file directly to Moodle.

### Tips

- You may pre-prepare materials (e.g., set up Git repositories or branches in advance).
- Speak as if you're explaining these concepts to a colleague who’s **familiar with Git** but **not very experienced**.  
  Aim for clarity and detail, not just correctness.
- Visuals and terminal demos are recommended, but are not required — clarity of explanation matters most.

## Marking rubric

* Technical content of each question: 5 points each (total 10 points)
* Explaining "why": 3 points
* Overal clarity and communication: 2 points

1 mark is deducted for every 30 seconds over the 10 minute time limit (maximum 3 mark deduction). A 10 minute 12 second video thus has a maximum of 14 marks.

**Total: 15 marks**