---
title: 'ETC5513: Collaborative and Reproducible Practices'
subtitle: "Assignment 1"
author: "Michael Lydeamore"
date: today
format:
    html:
        embed-resources: true
---


```{r setup}
#| include: false
#| eval: true
source("setup.R")
```

```{r}
#| echo: false

total_marks <- 0

add_marks <- function(amount) {
    total_marks <<- total_marks + amount

    amount
}

```

```{r, echo = FALSE, eval = file.exists("tutorial.css")}
htmltools::includeCSS("tutorial.css")
```


## `r emo::ji("target")` Objectives

* Working on a reproducible  Rstudio project
* Produce a html report using an qmd file and explore  YAML themes to define your prefer template
* Practice markdown syntax
* Practice R coding
* Explore R chunk options to customize your report template
* Create html tables, add table captions and  refer to them in the report text as described in Week 4
* Create simple figures to visualize the data, add figure captions and  refer to the figures in the report text as you learned in Week 4
* Demonstrate that you are able to clone a GitHub repository locally and synchronize the changes between your local and remote repositories.
* Show that you can create meaningful Git commits so that the changes and the history of the project can be recorded and tracked.

::: {.callout-important}
This is an **individual** assignment.

The final PDF report can not have more than 5 pages (not including the appendix).

You cannot use a dataset that has been used for another assignment.
:::

## Part A: Setting up version control

In this assignment, you need to create a project that will be able to produce a reproducible HTML report. For the report, you will each have your own unique dataset to work on. Your dataset will be in the `data/` folder on the GitHub repository.

I will push these datasets to your repos periodically, as you each create the repo. If your dataset is not there, please let me know and I will tend to it as soon as possible.

Your reproducible report should be created using a Quarto file in Rstudio  and needs to be rendered into a HTML file. The report must knit into HTML without any errors.

You will be working with a GitHub repository for this assignment. We will use GitHub Classroom, where I have set up some of the structure for you. Please join the classroom [here](https://classroom.github.com/a/5fkkugX_). Make sure to choose your Monash username from the list so we can find your assignment.

### Repository setup (`r add_marks(6)` points)

Clone the repository created by GitHub classroom onto your computer as we have done in lectures and tutorials (1 point).

Once you have cloned the repository to your computer, make sure to add all the files in the upcoming section, and use **relevant, clear commit messages** (5 points).

::: {.callout-caution}
The GitHub repo will appear in the GitHub classroom space. **Do not work in or create a different repository for this assignment**.
:::


## Part B: Creating a reproducible report

There is some pre-made structure in the repository. Open the folder in Positron as we have done in class to work on.

### R code chunk for loading libraries (`r add_marks(3)` points)

Create a new Quarto file. This file is where we will create the report for the rest of this assignment, so make sure to give it a sensible name (1 point).

Load all the libraries you will use in the report in an R chunk located at the beginning of your Quarto file. _Make sure you set the options so that you do not display any R code, messages, or warnings in the rendered HTML document (for this chunk)_ (1 point).

Set the YAML so that the report will be output as a HTML and PDF file.

### Introduction section (`r add_marks(2)` points)

Using markdown, write a 4 sentence **maximum** motivation of what you are going to research and why. _Make sure it is relevant to your dataset_.

### Research Question section (`r add_marks(2)` points)

Using markdown, discuss in 3 sentences **maximum**, the specific question that you are going to investigate or answer in this report using your selected data.

### Dataset Introduction section (`r add_marks(3)` points)

In this section, briefly describe your data (i.e. what the data is measuring or recording) in five sentences **maximum** using markdown.

To do this, you will need to clean your dataset. Include a description of this cleaning process (not the code) in the report. The code to clean the dataset _must_ be included in the Quarto file, but not in the report.

### Dataset Description subsection (`r add_marks(5)` points)

Create a _subsection_ that will report details about your data. You must include the size of the dataset such as the number of observations, variables and variable types. You must include the following:

* A sentence that includes _inline R code_ describing the number of variables and observations in your dataset.
* Using the function `head()`, display the first two rows of data to show the types of variables that are in the dataset (i.e. numeric, character/factor etc).

Create two other summaries of your data, one as a plot and one as a table. Examples include counts of certain variables in groups, or summary statistics of numeric variables. Make sure these summaries are providing a broader context to the report and are not just arbitrary commentaries.

## Results section (`r add_marks(5)` points)

Using visualisations of the data, discuss the answer to your research questions. You must:

* Create 2 figures maximum of your data that will help you answer your research question. Each figure must have a caption using the options inside the R code chunk. Create the figures using the `ggplot2` package.
* The figures must have captions, and must be referred to in the text of the results section.

As well as the figures, you must also include a paragraph describing these results and how they link back to your research question. Remember, you can use inline code to extract certain numbers automatically.

## Marking Rubric

In addition to the points as described above, you will be graded on your:

* Issues with spelling and grammar (up to -3 points).
* R code style (i.e. spacing, variable names) (`r add_marks(2)` points)
* Report quality: Sections in the report are connected and aligned with the research question in a coherent way (`r add_marks(2)` points).

Maximum grade: `r total_marks` points.

## The usage of AI

You may use Generative AI (such as ChatGPT) to _correct your English_ or to help with your R code (for example to find bugs or ask for enhancements to _your existing code_). However, if you use ChatGPT you must declare it in a separate qmd file called  `appendix.qmd`, and display screenshots of your AI queries and interactions related to this assignment. The appendix does not count towards your page limit.

You **cannot** use ChatGPT to generate content for this assignment from scratch, including code.

Monash University supports the responsible and ethical use of generative AI. For more info please refer to [Monash Policy and practice guidance around acceptable and responsible use of AI technologies](https://www.monash.edu/learning-teaching/teachhq/Teaching-practices/artificial-intelligence/policy-and-practice-guidance-around-acceptable-and-responsible-use-of-ai-technologies).

## Assignment Submission

The report must be rendered to HTML and PDF. The PDF cannot have a length of more than 5 pages (excluding the appendix).

**You do not need to upload _anything_ to Moodle. All marking will occur directly from your GitHub repositories**.

## Plagiarism

Monash University is committed to honesty and academic integrity. There are serious consequences for plagiarism and collusion. If plagiarism and/or collusion is detected further actions will be taken according to Monash University policy and procedures. More info here:

https://www.monash.edu/students/admin/policies/academic-integrity

You cannot re-use assignments that have been submitted or used in  other units.